Relational Parametricity for Algebraically Indexed Types

### 2012-05-08 paper/paper.tex
Add Andrew to author list, and alphabetise the authors

\usepackage[usenames]{color}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Patricia Johann, Neil Ghani},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}

@@

\authorinfo{Robert Atkey\and Patricia Johann\and Neil Ghani}
           {University of Strathclyde}
           {\{Robert.Atkey,Patricia.Johann,Neil.Ghani\}@cis.strath.ac.uk}

>>>>

\usepackage[usenames]{color}
\definecolor{citationcolour}{rgb}{0,0.4,0.2}
\definecolor{linkcolour}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            urlcolor=linkcolour,
            linkcolor=linkcolour,
            citecolor=citationcolour,
            pdftitle=Relational Parametricity for Algebraically-Indexed Types,
            pdfauthor={Robert Atkey, Neil Ghani, Patricia Johann, Andrew Kennedy},
            pdfkeywords={}}  
\def\sectionautorefname{Section}
\def\subsectionautorefname{Section}

@@

\authorinfo{Robert Atkey\and Neil Ghani\\\and Patricia Johann}
           {University of Strathclyde}
           {\{Robert.Atkey,Neil.Ghani,Patricia.Johann\}@cis.strath.ac.uk}

\authorinfo{Andrew Kennedy}
           {Microsoft Research}
           {}
